Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2019-06-17 thesis/abstract.tex
removing comments

\vskip.35in
{\large Andrew J. Emerick} \\
\vskip.35in
\end{center}
Motivated by the desire to investigate two of the largest outstanding problems in galactic evolution -- stellar feedback and galactic chemical evolution --
%In this \thesis
we develop the first set of galaxy-scale simulations that simultaneously follow star formation with individual stars and their associated multi-channel stellar feedback and multi-element metal yields. We developed these simulations to probe the way in which stellar feedback, including stellar winds, stellar radiation, and supernovae, couples to the interstellar medium (ISM), regulates star formation, and drives outflows in dwarf galaxies. We follow the evolution of the individual metal yields associated with these stars in order to trace how metals mix within the ISM and are ejected into the circumgalactic and intergalactic media (CGM, IGM) through outflows. This study is directed with the ultimate goal of leveraging the ever increasing quality of stellar abundance measurements within our own Milky Way galaxy and in nearby dwarf galaxies to understand galactic evolution.

@@

Using these simulations, we investigate the role that stellar radiation feedback plays in the evolution of low mass dwarf galaxies.
% a fiducial, full-physics simulation, second, a simulation with ionizing radiation restricted to the region immediately around massive star particles, and third, a simulation with no ionizing radiation feedback. I
In this regime, we find that the local effects of stellar radiation (within $\sim$ 10~pc of the massive, ionizing source star) act to regulate star formation by rapidly destroying cold, dense gas around newly formed stars. For the first time, we find that the long-range radiation effects far from the birth sites are vital for carving channels of diffuse gas in the ISM which dramatically increase the effect of supernovae. We find this effect is necessary to drive strong winds with significant mass loading factors and has a significant impact on the metal content of the ISM.

>>>>

\vskip.35in
{\large Andrew J. Emerick} \\
\vskip.35in
\end{center}
Motivated by the desire to investigate two of the largest outstanding problems in galactic evolution -- stellar feedback and galactic chemical evolution -- we develop the first set of galaxy-scale simulations that simultaneously follow star formation with individual stars and their associated multi-channel stellar feedback and multi-element metal yields. We developed these simulations to probe the way in which stellar feedback, including stellar winds, stellar radiation, and supernovae, couples to the interstellar medium (ISM), regulates star formation, and drives outflows in dwarf galaxies. We follow the evolution of the individual metal yields associated with these stars in order to trace how metals mix within the ISM and are ejected into the circumgalactic and intergalactic media (CGM, IGM) through outflows. This study is directed with the ultimate goal of leveraging the ever increasing quality of stellar abundance measurements within our own Milky Way galaxy and in nearby dwarf galaxies to understand galactic evolution.

@@

Using these simulations, we investigate the role that stellar radiation feedback plays in the evolution of low mass dwarf galaxies. In this regime, we find that the local effects of stellar radiation (within $\sim$ 10~pc of the massive, ionizing source star) act to regulate star formation by rapidly destroying cold, dense gas around newly formed stars. For the first time, we find that the long-range radiation effects far from the birth sites are vital for carving channels of diffuse gas in the ISM which dramatically increase the effect of supernovae. We find this effect is necessary to drive strong winds with significant mass loading factors and has a significant impact on the metal content of the ISM.
